Supplementary material

### 2017-10-24 Manuscript/ms.tex
Tweaking conclusions

Mosquito surveillance is a valuable tool in managing dengue fever, but is most powerful when integrated into a larger modeling framework.
We have developed a simple yet realistic mechanistic model of dengue fever spread that allows us to combine mosquito and clinical surveillance to estimate the latent mosquito demographic rates that govern the critical bottleneck between mosquito abundance and human disease.
That we have done this in a fully hierarchical Bayesian framework allows for a thorough accounting of uncertainty that can be carried through to the evaluation of different control strategies.
This combination of model features meets many of the recommendations of \cite{Morrison2008, Achee2015} for developing more effective, biologically grounded, and data-driven dengue control policies and offers a building block on which these tools can be further developed in the future.

>>>>

Mosquito surveillance is a valuable tool in managing dengue fever, but is most powerful when integrated into a larger modeling framework.
We have developed a simple yet realistic mechanistic model of dengue fever spread that allows us to combine mosquito and clinical surveillance to estimate the latent mosquito demographic rates that govern the critical bottleneck between mosquito abundance and human disease.
The mechanistic framework allows us to capture important lags and feedbacks in the transmission process and to identify critical intervention points that would not be apparent otherwise.
The fully hierarchical Bayesian framework in which the mechanistic model is embedded allows for a thorough accounting of uncertainty that can be carried through to the evaluation of different control strategies.
This combination of model features meets many of the recommendations of \cite{Morrison2008, Achee2015} for developing more effective, biologically grounded, and data-driven dengue control policies and offers a building block on which these tools can be further developed in the future.
